FoRTE baseline

### 2019-10-25 analysis/paper/paper.Rmd
Draft analysis of results text; rearrange results

@@

<!-- TODO Use a logarithmic, rather than a linear fit? -->

>>>>

First, we evaluated the impact of model structure independent of any changes to parameters by comparing predictions of average annual net primary productivity (NPP) and summer (June, July, August) total leaf area index (LAI) across model structures while holding ED-2.2 parameters at their default values (Figure 1).
To understand the physical and ecological mechanisms underlying these differences, we also compared the cohort-level composition, height, and canopy radiation profiles in these simulations in four stages of the simulation (Figure 2).

Second, we compared simulations with ED-2.2 default parameters against simulations using median parameter estimates from a trait meta-analysis (Figure 3).
Here, we looked predictions of annual mean C fluxes (gross and net primary productivity, and autotrophic and heterotrophic respiration; Figure 4) and of summer LAI by PFT (Figure 5).

Third, we considered the full range of parameter uncertainty by looking at predictions across all parameter ensemble members.
We begin with predictions annual mean NPP and summer mean total LAI across all parameters and structures and compare these results to contemporary (averaged over years TODO) observations of NPP and LAI at UMBS.
We look at these variables independently as time series (Figure 6) and as joint predictions in three years (Figure 7).
We then consider impacts on composition by looking at predicted PFT fractions of total aboveground biomass (AGB) at four different years in the simulation (Figure 8) and at time series of LAI by PFT for five parameter combinations spanning the range of predicted ecological outcomes (Figure 9).

Finally, we assessed which parameters contributed the most to parameter uncertainty for each model structure.
We did this by performing a sensitivity and variance decomposition analysis following @lebauer_2013_facilitating, @dietze_2014_quantitative, and @raczka_2018_what.
Briefly, this analysis contains uses a spline to estimate the relationship between individual parameters and output variables and then uses these splines to predict the variance in the output variable attributable to individual parameters ("partial variance").
For more details, see @lebauer_2013_facilitating.

First, we assessed how ED-2.2 predictions of plot-level ecosystem properties and composition varied across model structures and parameter values.
For plot-level ecosystem properties, we examined mean annual gross (GPP) and net primary productivity (NPP), and autotrophic (RA) and heterotrophic respiration (RH), as well as total leaf area index (LAI) averaged June-August.
We compared predicted NPP and LAI values against measurements of NPP and LAI at UMBS averaged over years XXXX-YYYY. <!-- TODO -->
Although these observations occurred later than the years of the simulation, we found that the distributions of ED-2.2 predictions of NPP and LAI were relatively stable after 1975 and therefore constituted a reasonable approximation of what ED-2.2 would have predicted out to the present day.
For ease of interpretation, we only show the top eight parameters in terms of partial variance for every model configuration.

For composition, we looked at annual means of summer aboveground biomass and leaf area index

@@
